Labor Markets and Technological Change: Evidence from Electronic Health Records

### 2021-11-01 Presentations/ThirdYearPaperpres.tex

\begin{alertblock}{Quality Improvement}
\begin{itemize}
    \item Improved efficiency, patient safety improvements, physicians have decision support that could prevent unnecessary complications, etc.
    \item Significant policy push for EHR implementation: HITECH Act, 2008 provided financial incentive for hospitals to implement EHRs 
\end{itemize}
\end{alertblock}

@@

\textcolor{blue}{The percentage of hospitals with basic EHR capability rose from 9$\%$ in 2008 to 84$\%$ in 2015.} \scriptsize (Health IT Dashboard)

@@

        \color{blue}
        \underline{ Contribution }
        \vspace{1mm}

        \color{blue}
        Speaks to this question in a particular setting 
            \begin{itemize}
            \color{blue}
                \item Important because health care spending is extremely high
                \item Important to think about physician labor markets because of shortages and access to care issues
            \end{itemize}

@@

\begin{frame}{Variables}
Labor Market Outcomes:
\vspace{-2mm}
\begin{itemize}
    \item Patients visited in hospitals
    \item \color{gray} Maintaining billable activity only outside of hospitals
    \item \color{gray} Level of billable activity outside of hospitals
    \item \color{gray} Retirement/leaving the labor force
\end{itemize}

>>>>

\begin{alertblock}{Quality Improvement}
\begin{itemize}
    \item Improved efficiency, patient safety improvements, physicians have decision support that could prevent unnecessary complications, etc.
\end{itemize}
\end{alertblock}

@@

Significant policy push for EHR implementation: HITECH Act, 2008 provided financial incentive for hospitals to implement EHRs
\begin{itemize}
    \item \textcolor{blue}{The percentage of hospitals with basic EHR capability rose from 9$\%$ in 2008 to 84$\%$ in 2015.} \scriptsize (Health IT Dashboard)
\end{itemize}

@@

        \color{blue}
        \underline{ Contribution }

        \vspace{1mm}

            \begin{itemize}
            \color{blue}
                \item Important because health care spending is extremely high
                \item Important to think about physician labor markets because of shortages and access to care issues
            \end{itemize}

@@

\begin{frame}{Variables}
Labor Market Outcomes:
\begin{itemize}
\item Productivity:
\begin{itemize}
    \item Patients visited in hospitals
\end{itemize}
\end{itemize}
\begin{itemize}
\item Retirement
\end{itemize}
\begin{itemize}
\item Work Setting:
\begin{itemize}
    \item \color{gray} Maintaining billable activity only outside of hospitals
    \item \color{gray} Level of billable activity outside of hospitals
\end{itemize}
\end{itemize}
